---
title: "Genetic Diversity Results"
author: "C. E. Moore"
output: 
  pdf_document:
    latex_engine: pdflatex
urlcolor: blue
header-includes:
  \usepackage{helvet}
  \renewcommand{\familydefault}{\sfdefault}
---
Last updated on `r Sys.Date()`  
  
*Note: Microsat data previously formatted from geneious output using 01a_DataPrep.R and then filtered for missing data in 10_MicrosatSummary.Rmd*  

**Contents:**  
1. Allelic Richness  
2. Hobs & Hexp  
3. Allele frequencies  
4. Effective population size  
5. Inbreeding  
  
```{r paths and data load, echo=FALSE, message=FALSE}
## packages
library(adegenet); library(ape); library(pegas); library(knitr); library(tidyverse); library(cowplot)

## home path
PATH <- "/home/chloe9mo/Documents/Projects/temporal_aztreefrog"

source(file = paste0(PATH, "/code/01c_DataLoad.R"))
```
**Loaded packages:** `r (.packages())`  

***  
# Rarefied Allelic Richness
``` {r AR, echo=FALSE}
#for rarefied ->  finds lowest valid sample size across pops + loci and multiplies it by the ploidy (2)
ar.list <- list()

for (i in 1:length(ind.list)) {
  
  ind.ar <- allelicrichness(as.loci(ind.list[[i]]), pop = as.loci(ind.list[[i]])$population, method = "rarefaction")
  cat(ind.names[[i]], "\n")
  m.ar <- apply(ind.ar, 1, mean)
  cat(m.ar, "\n")
  m.ar <- as.data.frame(m.ar) %>% mutate(pop = row.names(.))
  m.ar$year <- sub(".*(\\d+{4}).*$", "\\1", ind.names[[i]])
  ar.list[[i]] <- m.ar
  cat("---------------------------", "\n")
  
}

# ar.list <- ar.list[-c(1,2)]
ar.div <- bind_rows(ar.list) %>%
  mutate(group = case_when(year == "All Yrs - Indiv x Pop" ~ "All_Yrs",
                           year == "All Yrs - Indiv x Year" ~ "All_Pops",
                           year == "2014" ~ "2014",
                           year == "2019" ~ "2019",
                           year == "2021" ~ "2021")) %>%
  arrange(pop, group) %>%
  relocate(pop, group) %>% select(-year)

write.csv(ar.div, file = paste0(PATH, "/results_tables/allelic_richness.csv"), row.names = F)
```
```{r theme set up, echo=F}
dtheme <- list(
  geom_line(aes(color=pop)),
  geom_point(aes(color=pop)),
  scale_color_manual(values = aztf.pal),
  scale_x_discrete(expand = c(0.01,0.01)),
  theme(panel.background = element_blank(),
        panel.border = element_blank(),
        panel.grid = element_line(color="#E5E4E2"),
        legend.key = element_blank(),
        legend.text = element_text(size=15),
        legend.title = element_text(size = 15),
        plot.title = element_text(face = "bold", size = 18),
        axis.title = element_text(size=15),
        axis.text = element_text(size=13),
        axis.line.x.bottom = element_line(color="black"),
        axis.line.y.left = element_line(color="black"))
)
```

``` {r ar fig, echo=F, fig.align="center", eval=F}
p.ar <- ggplot(data = ar.div %>% filter(!group %in% c("All_Yrs", "All_Pops")), aes(x=group, y=m.ar, group=pop)) +
  labs(x="Sample Year", y="Rarefied Allelic Richness") +
  dtheme +
  theme(title = element_blank(),
        legend.position = "none")
p.ar
ggsave(filename = paste0(PATH, "/figures/delta_allelicrichness_nolegend.png"), plot = p.ar, width = 3, height = 5.45)
```
\begin{figure}[!h]
\centering
\includegraphics[width=0.5\textwidth]{"/home/chloe9mo/Documents/Projects/temporal_aztreefrog//figures/delta_allelicrichness_nolegend.png"}
\caption{Change in allelic richness over time.}
\end{figure}

***  

# Observed & Expected Heterozygosity  
``` {r hobs hexp, echo=FALSE, results='asis'}
div.list <- list()
for (i in 1: length(ind.list)) {
  
  # separate by population
  Hobs <- t(sapply(seppop(ind.list[[i]]), function(ls) summary(ls)$Hobs))
  Hexp <- t(sapply(seppop(ind.list[[i]]), function(ls) summary(ls)$Hexp))
  
  cat(" exp. H for", ind.names[[i]], "\n")
  print(kable(as.data.frame(round(Hexp, 2))))
  cat("\n", " obs. H for", ind.names[[i]], "\n")
  print(kable(as.data.frame(round(Hobs, 2))))
  cat("\n")
  
  a.hexp <- as.data.frame(apply(Hexp, 1, mean)) %>% rownames_to_column(var = "pop")
  ah <- as.data.frame(apply(Hobs, 1, mean)) %>% rownames_to_column(var = "pop") %>% left_join(., a.hexp, by="pop")
  names(ah) <- c("pop", "H_obs", "H_exp")
  ah <- ah %>% mutate(H_diff = if_else(H_obs - H_exp > 0, "Hobs higher", "Hobs lower"))
  
  print(kable(ah, caption = ind.names[[i]]))
  ah <- ah %>% mutate(year = sub('.*(?=.{4}$)', '', ind.names[[i]], perl=T))
  div.list[[i]] <- ah
  
  # par(mfrow = c(2,1))
  # barplot(ah$H_exp ~ ah$pop, beside = T, ylim = c(0,1), col = "grey", ylab = "Expected heterozygosity", xlab = "Group")
  # barplot(ah$H_obs ~ ah$pop, beside = T, ylim = c(0,1), col = "grey", ylab = "Observed heterozygosity", xlab = "Group")
  
  cat("\n", "global observed for", ind.names[[i]], "=", mean(Hobs))
  cat("\n", "-------------------------------------------", "\n", "\n")
  
}

g.hobs <- data.frame(unlist(ind.names), stringsAsFactors = F) %>% 
  add_column(global_Hobs = NA) %>% rename(group = unlist.ind.names.)

for (i in 1:length(ind.list)) {
  
  Hobs <- t(sapply(seppop(ind.list[[i]]), function(ls) summary(ls)$Hobs))
  g.hobs[g.hobs$group == ind.names[[i]],]$global_Hobs <- mean(Hobs)
  
}

kable(g.hobs, caption="Global Observed Heterozygosity")
#  observed frequently lower than expected, some pops inbreeding?
#  high amounts of diversity

div.full <- bind_rows(div.list) %>%
  mutate(group = case_when(year == " Pop" ~ "All_Yrs",
                           year == "Year" ~ "All_Pops",
                           year == "2014" ~ "2014",
                           year == "2019" ~ "2019",
                           year == "2021" ~ "2021"),
         hdiff = H_exp - H_obs) %>%
  arrange(pop, group) %>%
  relocate(pop, group) %>% select(-year)
write.csv(div.full, file = paste0(PATH,"/results_tables/hdiv_summary.csv"), row.names = F)
```

# Change in heterozygosity over time  
```{r, echo=F, message=F}
div.list <- div.list[-c(1,2)]
hdiv <- bind_rows(div.list)
hdiv <- hdiv %>% mutate(hdiff = H_exp - H_obs)

p.ho <- ggplot(data = hdiv, aes(x=year, y=H_obs, group=pop)) +
  labs(x="Sample Year", y="Obs. Heterozygosity") +
  dtheme +
  scale_y_continuous(limits = c(0.58, 0.755), breaks = c(0.60, 0.65, 0.70, 0.75)) +
  theme(title = element_blank(),
        legend.position = "none")
p.he <- ggplot(data = hdiv, aes(x=year, y=H_exp, group=pop)) +
  labs(x="Sample Year", y="Exp. Heterozygosity") +
  dtheme +
  scale_y_continuous(limits = c(0.58, 0.755), breaks = c(0.60, 0.65, 0.70, 0.75)) +
  theme(title = element_blank(),
        legend.position = "none")
p.hd <- ggplot(data = hdiv, aes(x=year, y=hdiff, group=pop)) +
  geom_rect(xmin = -Inf, xmax = Inf, ymin = -0.1, ymax = 0, fill="blue", alpha = 0.005) +
  geom_rect(xmin = -Inf, xmax = Inf, ymin = 0, ymax = 0.1, fill="red", alpha = 0.005) +
  # geom_hline(yintercept = 0, linetype="dashed", color="red") +
  scale_y_continuous(limits = c(-0.08, 0.08), breaks = c(-0.08, -0.04, 0, 0.04, 0.08)) +
  labs(x="Sample Year", y=bquote(~H[e]~ '-' ~H[o]~ '')) +
  dtheme +
  theme(title = element_blank(),
        legend.position = "none")

plot_grid(p.ho, p.he, p.hd, nrow = 1, ncol = 3, labels = "AUTO", rel_widths = c(1, 1, 1.25))

ggsave(filename = paste0(PATH, "/figures/delta_Ho.png"), plot = p.ho, width = 3, height = 5.45)
ggsave(filename = paste0(PATH, "/figures/delta_He.png"), plot = p.he, width = 3, height = 5.45)
ggsave(filename = paste0(PATH, "/figures/delta_diffH_nolegend.png"), plot = p.hd, width = 3, height = 5.45)
```

***
# Allele frequencies
**Note:** With 17 loci, freq. should add up to 17. Second table on each set is a check.  
  
``` {r, echo=F, message=F}
for (i in 1:length(pop.list)) {
  
  cat(pop.names[[i]], "\n")
  freq <- adegenet::makefreq(pop.list[[i]])
  cat("\n", "There are ", ncol(freq), " alleles.", "\n", "Looking at freq of first 10.", "\n")
  print(round(freq[, 1:10], 2))
  cat("\n", "Checking they add to 17:", "\n")
  print(apply(freq, 1, sum))
  cat("\n", "==============================================", "\n")
  
}

```

***
# Effective population size

``` {r, echo=F, message=F, fig.align="center"}
Net <- read.csv(paste0(PATH, "/results_tables/Ne_Table_nosibs.csv"))
Net <- Net %>% 
  mutate(year = substr(Pop, 1, 4), pond = as.integer(gsub("^[0-9]{4}.", "", Pop))) %>%
  select(-Notes) %>% 
  mutate(year = ifelse(year == 2015, 2014, year))
Net <- Net %>% mutate(pond = factor(pond)) %>%
  mutate(pond = fct_relevel(pond, c("1", "3", "4", "6", "7", "8", "9", "10", "16")),
         Ne = ifelse(Ne == "Infinite", 800, Ne)) %>% #10000 was the replacement in Mims 2016
  mutate(across(starts_with("Ne"), as.numeric))

dNet <- Net %>% 
  select(pond, year, Ne) %>% 
  pivot_wider(id_cols = pond, names_from = year, values_from = Ne)
names(dNet) <- c("pond", "n2014", "n2019", "n2021")
dNet <- dNet %>%
  mutate(d14_19 = ((n2019 - n2014)/n2014)*100,
         d19_21 = ((n2021 - n2019)/n2019)*100, 
         d14_21 = ((n2021 - n2014)/n2014)*100)

kable(Net %>% select(year, pond, Ne, Ne.Low, Ne.High), caption = "Effective population size of all ponds and years as calculated using the LD method in NeEstimator v2")

ggplot(data = Net, aes(x=year, y=Ne, group=pond)) +
  geom_line(aes(color=pond)) +
  geom_point(aes(color=pond)) +
  scale_color_manual(values = aztf.pal, aesthetics = "color") +
  labs(x="Sample Year", y="Effective Population Size (Ne)", title = "Ne change over time") +
  coord_cartesian(ylim = c(0,400)) +
  theme_minimal() +
  scale_x_discrete(expand = c(0.01,0.01))
```

``` {r, echo=F, message=F, fig.align="center", eval=F}
library(sf); library(ggmap); library(cowplot); library(RColorBrewer)
sp.ne <- coord %>%
  left_join(Net, by=c("year_pop" = "Pop")) %>%
  filter(!is.na(Ne)) %>%
  st_as_sf(coords=c("lon", "lat"), crs=st_crs(32612)) %>%
  mutate(Ne = ifelse(Ne == "Inf", NA, Ne))#WGS 84 / UTM zone 12N
sp.ne <- sp.ne %>% left_join(dNet %>% select(pond, d14_19, d19_21, d14_21), by = "pond")

e <- as.data.frame(as.matrix(st_bbox(sp.ne))) %>% rownames_to_column(var = "name") %>% pivot_wider(names_from = name, values_from = V1)
e[,c(1:2)] <- e[,c(1:2)] - 0.02 #1 degrees diff = ~100 km
e[,c(3:4)] <- e[,c(3:4)] + 0.02

az.base <- get_map(location = c(left = e$xmin, bottom = e$ymin, right = e$xmax, top = e$ymax),
                   maptype = "terrain")

sp.ne.noinf <- sp.ne %>% filter(Ne < 350)
sp.ne.inf <- sp.ne %>% filter(Ne > 350) %>% mutate(Ne = Inf)
sp.dne <- sp.ne %>% select(pond, d14_19, d19_21, d14_21) %>% distinct()

ggaztf_theme <- list(
  coord_sf(datum = sf::st_crs(sp.ne)),
  # scale_fill_viridis_c(option="magma", guide = "legend", 
  #                      limits=c(min(sp.ne$Ne, na.rm = T), max(sp.ne$Ne, na.rm = T)),
  #                      breaks = c(10, 60, 110, 160, 210, 260, 310, 540)),
  scale_fill_gradient(low = "#CC4E00", high = "#FFF2EB",  guide = "legend",
                      limits=c(min(sp.ne.noinf$Ne, na.rm = T), max(sp.ne.noinf$Ne, na.rm = T)),
                      # breaks = round(seq(range(sp.ne.noinf$Ne)[1], range(sp.ne.noinf$Ne)[2], length.out = 5), 0)),
                      breaks = c(10, 50, 100, 200, 300)),
  scale_size_continuous(range = c(4, 14), guide = "legend",
                        limits=c(min(sp.ne.noinf$Ne, na.rm = T), max(sp.ne.noinf$Ne, na.rm = T)),
                        # breaks = round(seq(range(sp.ne.noinf$Ne)[1], range(sp.ne.noinf$Ne)[2], length.out = 5), 0)),
                      breaks = c(10, 50, 100, 200, 300)),
  labs(x = "Longitude", y = "Latitude"),
  theme(
        panel.background = element_blank(),
        panel.border = element_rect(fill=NA, color = "black"),
        legend.key = element_blank(),
        legend.text = element_text(size=18),
        legend.title = element_text(size = 18),
        plot.title = element_text(face = "bold", size = 18),
        axis.title = element_text(size=15),
        axis.text = element_text(size=13))
  )

p14 <- ggmap(az.base) +
  geom_sf(data = sp.ne %>% 
            group_by(pond) %>%
            filter(!any(year == '2014')) %>%
            select(geometry) %>% 
            unique(),
          shape=13, size=6, color="black", inherit.aes = F) +
  geom_sf(data = sp.ne.noinf %>% filter(year == '2014'), aes(size = Ne, fill = Ne), shape=21, inherit.aes = F) +
  geom_sf(data = sp.ne.inf %>% mutate(Ne = "Inf"), aes(color=Ne), shape=16, size=12, alpha=0, inherit.aes = F) +
  geom_sf(data = sp.ne.inf %>% mutate(Ne = "Inf"), shape=21, color = "black", fill="transparent", size=12, alpha=0, inherit.aes = F) +
  scale_color_manual(values=c("white")) +
  ggtitle("2014 Effective Population Size") +
  ggaztf_theme +
  theme(legend.position = "bottom") +
  guides(color = guide_legend(title = NULL, order = 2, override.aes = list(shape=21, size=16, fill="white", color="black", alpha=1), label.position = "bottom"), 
         size = guide_legend(order=1, label.position = "bottom"), 
         fill=guide_legend(order=1, label.position = "bottom"))

p19 <- ggmap(az.base) +
  geom_sf(data = sp.ne %>% 
            group_by(pond) %>%
            filter(!any(year == '2019')) %>%
            select(geometry) %>% 
            unique(),
          shape=13, size=6, color="black", inherit.aes = F) +
  geom_sf(data = sp.ne.noinf %>% filter(year == '2019'), aes(size = Ne, fill = Ne), shape=21, inherit.aes = F) +
  geom_sf(data = sp.ne.inf %>% mutate(Ne = "Inf"), aes(color=Ne), shape=16, size=12, alpha=0, inherit.aes = F) +
  geom_sf(data = sp.ne.inf %>% mutate(Ne = "Inf"), shape=21, color = "black", fill="transparent", size=12, alpha=0, inherit.aes = F) +
  scale_color_manual(values=c("white")) +
  ggtitle("2019 Effective Population Size") +
  ggaztf_theme +
  theme(axis.title = element_blank(), axis.text.y = element_blank(),
        legend.position = "bottom") +
  guides(color = guide_legend(title = NULL, order = 2, override.aes = list(shape=21, size=16, fill="white", color="black", alpha=1), label.position = "bottom"), 
         size = guide_legend(order=1, label.position = "bottom"), 
         fill=guide_legend(order=1, label.position = "bottom"))

p21 <- ggmap(az.base) +
  geom_sf(data = sp.ne %>% 
            group_by(pond) %>%
            filter(!any(year == '2021')) %>%
            select(geometry) %>% 
            unique(),
          shape=13, size=6, color="black", inherit.aes = F) +
  geom_sf(data = sp.ne.noinf %>% filter(year == '2021'), aes(size = Ne, fill = Ne), shape=21, inherit.aes = F) +
  geom_sf(data = sp.ne.inf %>% mutate(Ne = "Inf"), aes(color=Ne), shape=16, size=16, alpha=1, inherit.aes = F) +
  geom_sf(data = sp.ne.inf %>% mutate(Ne = "Inf"), shape=21, color = "black", fill=NA, size=16, alpha=1, inherit.aes = F) +
  scale_color_manual(values=c("white")) +
  ggtitle("2021 Effective Population Size") +
  ggaztf_theme +
  theme(axis.title = element_blank(), axis.text.y = element_blank(),
        legend.position = "bottom") +
  guides(color = guide_legend(title = NULL, order = 2, override.aes = list(shape=21, size=16, fill="white", color="black", alpha=1), label.position = "bottom"), 
         size = guide_legend(order=1, label.position = "bottom"), 
         fill=guide_legend(order=1, label.position = "bottom"))

p14
p19
p21

ggsave(filename = paste0(PATH, "/figures/Ne_map_2014.png"), plot = p14, width = 6.8, height = 6.7)
ggsave(filename = paste0(PATH, "/figures/Ne_map_2019.png"), plot = p19, width = 6.3, height = 6.5)
ggsave(filename = paste0(PATH, "/figures/Ne_map_2021.png"), plot = p21, width = 6.3, height = 6.5)


sp.dne <- sp.dne %>% 
  mutate(sy14_19 = if_else(d14_19 > 0, "pos", "neg"),
         sy19_21 = if_else(d19_21 > 0, "pos", "neg"),
         sy14_21 = if_else(d14_21 > 0, "pos", "neg")) %>%
  mutate(across(starts_with("d"), ~ abs(.x)))

blupal <- colorRampPalette(brewer.pal(9, "YlOrRd")[4:9])
redpal <- colorRampPalette(brewer.pal(9, "PuBu")[4:9])
maxdne <- round(max(sp.dne %>% select(starts_with("d")) %>% st_drop_geometry(), na.rm = T),0)
mindne <- round(min(sp.dne %>% select(starts_with("d")) %>% st_drop_geometry(), na.rm = T),0)

ggdne_theme <- list(
  coord_sf(datum = sf::st_crs(sp.dne)),
  scale_color_gradientn(colors = blupal(100), limits=c(mindne-9, maxdne+9)),
  scale_fill_gradientn(colors = redpal(100),  limits=c(mindne-9, maxdne+9)),
  scale_size_continuous(range = c(2, 12), guide = "legend",
                        limits=c(mindne-9, maxdne+9),
                        breaks = c(0, 500, 1000, 1500)),
  labs(x = "Longitude", y = "Latitude"),
  theme(panel.background = element_blank(),
        panel.border = element_rect(fill=NA, color = "black"),
        legend.key = element_blank(),
        legend.position = "bottom",
        legend.box = "vertical",
        legend.text = element_text(size=15),
        legend.title = element_text(size = 15),
        plot.title = element_text(face = "bold", size = 18),
        axis.title = element_text(size=15),
        axis.text = element_text(size=13)
        ),
  guides(fill = guide_legend(title = "pos. % change", order = 2, override.aes = list(size=c(2,7,9,12), shape=21, fill=redpal(4), color="black"), label.position="bottom"),
         color = guide_legend(title = "neg. % change", order = 1, label=F,  override.aes = list(size=c(2,7,9,12), shape=21, fill=blupal(4), color="black")),
         size = "none")
  )

p14_19 <- ggmap(az.base) +
  geom_sf(data = sp.dne %>% filter(is.na(d14_19)), shape=13, size=5, color="black", inherit.aes = F) +
  geom_sf(data = sp.dne %>% filter(sy14_19 == 'pos'), aes(size = d14_19, fill = d14_19), shape=21, color="transparent", inherit.aes = F) +
  geom_sf(data = sp.dne %>% filter(sy14_19 == 'neg'), aes(size = d14_19, color = d14_19), shape=16, inherit.aes = F) +
  geom_sf(data = sp.dne %>% filter(!is.na(d14_19)), aes(size = d14_19), shape=21, fill=NA, inherit.aes = F) +
  # geom_sf(data = sp.ne.inf %>% mutate(Ne = "Inf"), aes(color=Ne), shape=16, size=12, alpha=1, inherit.aes = F) +
  ggtitle("2014 to 2019 Ne Change") +
  ggdne_theme
p14_19

p19_21 <- ggmap(az.base) +
  geom_sf(data = sp.dne %>% filter(is.na(d19_21)), shape=13, size=5, color="black", inherit.aes = F) +
  geom_sf(data = sp.dne %>% filter(sy19_21 == 'pos'), aes(size = d19_21, fill = d19_21), shape=21, color="transparent", inherit.aes = F) +
  geom_sf(data = sp.dne %>% filter(sy19_21 == 'neg'), aes(size = d19_21, color = d19_21), shape=16, inherit.aes = F) +
  geom_sf(data = sp.dne %>% filter(!is.na(d19_21)), aes(size = d19_21), shape=21, fill=NA, inherit.aes = F) +
  # geom_sf(data = sp.ne.inf %>% mutate(Ne = "Inf"), aes(color=Ne), shape=16, size=12, alpha=1, inherit.aes = F) +
  ggtitle("2019 to 2021 Ne Change") +
  ggdne_theme
p19_21

p14_21 <- ggmap(az.base) +
  geom_sf(data = sp.dne %>% filter(is.na(d14_21)), shape=13, size=5, color="black", inherit.aes = F) +
  geom_sf(data = sp.dne %>% filter(sy14_21 == 'pos'), aes(size = d14_21, fill = d14_21), shape=21, color="transparent", inherit.aes = F) +
  geom_sf(data = sp.dne %>% filter(sy14_21 == 'neg'), aes(size = d14_21, color = d14_21), shape=16, inherit.aes = F) +
  geom_sf(data = sp.dne %>% filter(!is.na(d14_21)), aes(size = d14_21), shape=21, fill=NA, inherit.aes = F) +
  # geom_sf(data = sp.ne.inf %>% mutate(Ne = "Inf"), aes(color=Ne), shape=16, size=12, alpha=1, inherit.aes = F) +
  ggtitle("2014 to 2021 Ne Change") +
  ggdne_theme
p14_21
# 
# ggsave(filename = paste0(PATH, "/figures/Ne_change_map_14-19.png"), plot = p14_19)
# ggsave(filename = paste0(PATH, "/figures/Ne_change_map_19-21.png"), plot = p19_21)
# ggsave(filename = paste0(PATH, "/figures/Ne_change_map_14-21.png"), plot = p14_21)
```

\begin{figure}[!ht]
  \centering
  \includegraphics[width=0.4\textwidth]{"/home/chloe9mo/Documents/Projects/temporal_aztreefrog/figures/Ne_map_2014.png"}
  \includegraphics[width=0.4\textwidth]{"/home/chloe9mo/Documents/Projects/temporal_aztreefrog/figures/Ne_map_2019.png"}
  \includegraphics[width=0.4\textwidth]{"/home/chloe9mo/Documents/Projects/temporal_aztreefrog/figures/Ne_map_2021.png"}
  \caption{Individual year effective population size (LDNe).}
\end{figure}

\begin{figure}[!hb]
  \centering
  \includegraphics[width=0.4\textwidth]{"/home/chloe9mo/Documents/Projects/temporal_aztreefrog/figures/Ne_change_map_14-19.png"}
  \includegraphics[width=0.4\textwidth]{"/home/chloe9mo/Documents/Projects/temporal_aztreefrog/figures/Ne_change_map_19-21.png"}
  \includegraphics[width=0.4\textwidth]{"/home/chloe9mo/Documents/Projects/temporal_aztreefrog/figures/Ne_change_map_14-21.png"}
  \caption{Effective population size difference between years.}
\end{figure}

## Ne vs Sample Size  

``` {r, echo=F, eval=F}
coord <- read.csv(paste0(PATH, "/pond_coordinates.csv")) %>% st_as_sf(coords=c("lon", "lat"), crs=st_crs(32612))
sumdat <- read.csv(paste0(PATH,"/HYWR_multiyear_popsumm.csv"))
tot <- read.csv(paste0(PATH,"/multiyear_hywr_tracking.csv"))
tot14 <- tot %>% filter(Year.Sampled == '2014')
tot <- tot %>% filter(Plate_PM1 != "") %>% filter(Plate_PM1 != "--")
tot <- bind_rows(tot, tot14)

coord <- coord %>%
  select(-year_pop) %>%
  filter(pop %in% c("1", "3", "4", "6", "7", "8", "9", "10", "16")) %>%
  left_join(sumdat, by="pop") %>%
  mutate(pop = fct_relevel(factor(pop), c("1", "3", "4", "6", "7", "8", "9", "10", "16"))) %>%
  left_join(dNet, by=c('pop'='pond')) %>%
  distinct()
ns <- coord %>%
  select(pop, matches('2014|2019|2021'))
sumtot <- tot %>%
  select(Year.Sampled, Pond.Number) %>%
  count(Year.Sampled, Pond.Number) %>%
  pivot_wider(id_cols=Pond.Number, names_from = Year.Sampled, values_from=n) %>%
  replace(is.na(.), 0) %>%
  rename(t2014 = '2014',
         t2019 = '2019',
         t2021 = '2021',
         pop = Pond.Number) %>%
  filter(pop %in% ns$pop)
ns <- left_join(ns, sumtot, by='pop') %>% st_drop_geometry()
ns[is.na(ns)] <- 0
names(ns) <- c("pop", "y2014_NoSibs", "y2019_NoSibs", "y2021_NoSibs", "y2014_Ne", "y2019_Ne", "y2021_Ne", "y2014_Sibs", "y2019_Sibs", "y2021_Sibs")
ns[ns$pop == "16", "y2019_Sibs"] <- 12
gns <- ns %>% pivot_longer(cols = -pop) %>%
  mutate(year = gsub("\\D+", "", name),
         type = gsub(".*_", "", name)) %>%
  select(-name) %>% 
  pivot_wider(names_from = type, values_from = value) %>%
  mutate(ind_lost = Sibs - NoSibs)
write.csv(gns, file=paste0(PATH,"/results_tables/sample_count_summary.csv"), row.names = F)

sne.theme <- list(
  scale_color_manual(values = c("#CCCCCC", "#999999", "#333333"), aesthetics = "color"),
  theme(panel.background = element_blank(),
        axis.line.x = element_line(color = "black"),
        axis.line.y = element_line(color = "black"),
        panel.grid = element_line(color="#E5E4E2"),
        axis.title = element_text(size = 21),
        axis.text = element_text(size = 18))
)

ps <- ggplot(gns %>% filter(between(Ne, 1, 400))) +
# ggplot(gns %>% filter(between(Ne, 0, 400))) +
  geom_point(aes(x=Sibs, y=Ne, color=year)) +
  geom_smooth(method = "lm", formula='y~x', aes(x=Sibs, y=Ne, color=year), se=F) +
  geom_smooth(method = "lm", formula='y~x', aes(x=Sibs, y=Ne), linetype="dashed", color="red", se=F) +
  labs(x="Siblings Removed", y="Effective Population Size") +
  sne.theme
print(cor.test(gns$Sibs, gns$Ne, method = "pearson"))

pns <- ggplot(gns %>% filter(between(Ne, 1, 400))) +
# ggplot(gns %>% filter(between(Ne, 0, 400))) +
  geom_point(aes(x=NoSibs, y=Ne, color=year)) +
  geom_smooth(method = "lm", formula='y~x', aes(x=NoSibs, y=Ne, color=year), se=F) +
  geom_smooth(method = "lm", formula='y~x', aes(x=NoSibs, y=Ne), linetype="dashed", color="red", se=F) +
  labs(x="Siblings Not Removed", y="Effective Population Size") +
  sne.theme
print(cor.test(gns$NoSibs, gns$Ne, method = "pearson"))

plot_grid(ps, pns, align = "h")
# ggsave(filename = paste0(PATH,"/figures/NevsSibs.png"), plot = ps, width = 5, height = 5)
# ggsave(filename = paste0(PATH,"/figures/NevsNoSibs.png"), plot = pns, width = 5, height = 5)
```

\begin{figure}[ht!]
  \centering
  \includegraphics[width=0.4\textwidth]{"/home/chloe9mo/Documents/Projects/temporal_aztreefrog/figures/NevsNoSibs.png"}
  \includegraphics[width=0.4\textwidth]{"/home/chloe9mo/Documents/Projects/temporal_aztreefrog/figures/NevsSibs.png"}
  \caption{Relationship between effective population size and sample size.}
\end{figure}

# Inbreeding estimates  

``` {r inbreeding, echo=F, message=F, eval=F}
Fbar <- vector("list", length = length(ind.list))

#calc likelihood based estimation of inbreeding
for (i in 1:length(ind.list)) {

  temp <- inbreeding(ind.list[[i]], N=100)
  Fbar[[i]] <- sapply(temp, mean)

}

#compile into single dataframe
Fbar.t <- Fbar[[1]] %>%
  as.data.frame() %>%
  rownames_to_column("sample") %>%
  rename(Fbar = '.') %>%
  mutate(group = ind.names[[1]])
for (i in 2:length(Fbar)) {
  temp <- Fbar[[i]] %>%
    as.data.frame() %>%
    rownames_to_column("sample") %>%
    rename(Fbar = '.') %>%
    mutate(group = ind.names[[i]])
  Fbar.t <- bind_rows(Fbar.t, temp)
}

Fbar.t <- Fbar.t %>% 
  group_by(group) %>%
  mutate(n4 = sum(Fbar > 0.4))

ip <- ggplot(Fbar.t %>% filter(!grepl("All Yrs", group)), aes(x=Fbar)) +
  geom_histogram() +
  geom_vline(aes(xintercept=0.4), color="red", linetype="dashed") +
  facet_wrap(~ group) +
  theme_bw() +
  geom_text(data=Fbar.t %>% select(group, n4) %>% distinct() %>% filter(!grepl("All Yrs", group)), 
            aes(x=0.6, y=35, label=paste0("N > 0.4 = \n", n4)))

ggsave(paste0(PATH, "/figures/IndYear_InbreedingHist.png"), plot = ip)


table((Fbar.t %>% filter(Fbar > 0.4, !grepl("All Yrs", group)) %>% left_join(aztf %>% select(ID, pop, year), by = c("sample" = "ID")))$pop)


#look at plot of likelihood distribution
# F <- inbreeding(ind.list[[i]], res.type="function")[which(Fbar>0.4)]
# 
# plot(F$`2014-MCM-0032`, main=paste("Inbreeding of individual",names(F)),
# xlab="Inbreeding (F)", ylab="Probability density")
# plot(F$`2014-MCM-0056`, add=T, col="red")
# plot(F$`2014-MCM-0296`, add=T, col="blue")
```

\begin{figure}[hb!]
  \centering
  \includegraphics[width=0.6\textwidth]{"/home/chloe9mo/Documents/Projects/temporal_aztreefrog/figures/IndYear_InbreedingHist.png"}
  \caption{Estimate of individuals with high likelihood of inbreeding. Fbar > 0.4 indicates likely inbred. Population 8 most consistently has degree of inbreeding.}
\end{figure}
